---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Name Greta Recktenwald
  - Name Abby Hofschneider
  - Name Ayden Currier 
  - Name 4
  - Name 5

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---

```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)



file_path <- 'Goalies.csv'
Goalies <- read.csv(file_path)

```



# Introduction

About this project :clap:
This project is to show my understanding of data analytics and how to use R studio 
https://www.kaggle.com/datasets/open-source-sports/professional-hockey-database?select=Goalies.csv 


# Data

## Summary Statistics
```{r}
rmarkdown::paged_table(Goalies)

```

```{r}
skim(Goalies) %>%
  select(-n_missing)
```


## Visualization

What five players have the most goals scored against?
```{r}
library(dplyr)
top_5_goalies <- Goalies %>%
  arrange(desc(PostGA)) %>%
  head(5)

specific_goalies1 <- c("hrudeke01", "bannemu01", "daleyjo01", "hextaro01", 
                       "fleurma01")
top_5_data <- subset(Goalies, playerID %in% specific_goalies1)


ggplot(top_5_data, aes(x = playerID, fill = PostGA)) +
  geom_bar()

```
The player with `playerID` "bannemu01" showed the highest number of goals scored against


What five players have the most postseason wins?
```{r}
top_5_goalies_wins <- Goalies %>%
  arrange(desc(PostW)) %>%
  head(5)
print(top_5_goalies_wins)

specific_goalies2 <- c("barrato01", "belfoed01", "brodema01", "fleurma01", 
                       "fuhrgr01")
top_5_data2 <- subset(Goalies, playerID %in% specific_goalies2)


ggplot(top_5_data2, aes(x = playerID, fill = PostW)) +
  geom_bar()
```
The player with `playerID` "barrato01" showed the highest number of postseason wins



What is the relationship between goalie shutouts and wins?
```{r}
library(ggplot2)
ggplot(data = Goalies) +
  geom_point(mapping = aes(x = SHO, y = W))
```
There is a positive relationship between goalie shutouts and wins. So, if a goalie continues tp have shutouts, the teams chances of wining increase signifitcantly 
